A Derivative Tracking Model for Wind Power Forecast Error

### 2020-07-19 LaTeX_Code/Paper/aoas-template.tex
Added Marco comments
Added most marcos comments

\begin{figure}[H]
\centering
\includegraphics[width=0.485\textwidth]{plots/four_days/377.eps}\quad
\includegraphics[width=0.485\textwidth]{plots/four_days/417.eps}\\
%\quad\\
%\includegraphics[width=0.45\textwidth]{plots/four_days/437.eps}
%\includegraphics[width=0.45\textwidth]{plots/four_days/477.eps}
\caption{Four 24-hour segments with the wind power real production in Uruguay (orange line) recorded every ten minutes, and the hourly wind power production forecasted by provider A (blue line).}
  \label{fig:sample_data}
\end{figure}

@@

\begin{figure}[H]
\centering
  \includegraphics[width=0.485\textwidth]{plots/31.eps}\quad\includegraphics[width=0.485\textwidth]{plots/31_2.eps}
  \caption{Pointwise confidence bands fitted, for the same daily segment, through diffusion models without derivative tracking (plot on the left) and with derivative tracking (plot on the right).}
  \label{fig:derivative_tracking}
\end{figure}

@@

%---BEGIN APPENDIX---

\section{Appendix} \label{Appendix}

\subsection{The model}

@@

%---END APPENDIX---

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Single Appendix:                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{appendix}
%\section*{???}%% if no title is needed, leave empty \section*{}.
%\end{appendix}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Multiple Appendixes:                     %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{appendix}
%\section{???}
%
%\section{???}
%
%\end{appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Support information (funding), if any,   %%
%% should be provided in the                %%
%% Acknowledgements section.                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{Acknowledgements}
% The authors would like to thank ...
% 
% The first author was supported by ...
% 
% The second author was supported in part by ...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supplementary Material, if any, should   %%
%% be provided in {supplement} environment  %%
%% with title inside \textbf{} and short    %%
%% description below.                       %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{supplement}
%\textbf{???}.
%???.
%\end{supplement}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=0.485\textwidth]{plots/four_days/1.eps}\quad
\includegraphics[width=0.485\textwidth]{plots/four_days/3.eps}\\
%\quad\\
%\includegraphics[width=0.45\textwidth]{plots/four_days/437.eps}
%\includegraphics[width=0.45\textwidth]{plots/four_days/477.eps}
\caption{Two 24-hour segments with the normalized wind power real production in Uruguay (blue line) recorded every ten minutes, and the hourly wind power production forecasted by provider A (black line).}
  \label{fig:sample_data}
\end{figure}

@@

\begin{figure}[H]
\centering
  \includegraphics[width=0.485\textwidth]{plots/31_2.eps}\quad\includegraphics[width=0.485\textwidth]{plots/31.eps}
  \caption{Pointwise confidence bands fitted, for the same daily segment, through diffusion models without derivative tracking (plot on the left) and with derivative tracking (plot on the right).}
  \label{fig:derivative_tracking}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Single Appendix:                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendix}
\section*{}%% if no title is needed, leave empty \section*{}.

@@

\end{appendix}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Multiple Appendixes:                     %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{appendix}
%\section{???}
%
%\section{???}
%
%\end{appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Support information (funding), if any,   %%
%% should be provided in the                %%
%% Acknowledgements section.                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
This work was partially supported by the KAUST Office of Sponsored Research (OSR) under Award number URF/1/2584 -- 01 -- 01 in the KAUST Competitive Research Grants Program Round 8 and the Alexander von Humboldt Foundation.

% The authors would like to thank ...
% 
% The first author was supported by ...
% 
% The second author was supported in part by ...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supplementary Material, if any, should   %%
%% be provided in {supplement} environment  %%
%% with title inside \textbf{} and short    %%
%% description below.                       %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{supplement}

\sname{Supplement}
\stitle{DATA AND SIMULATIONS}
\slink[doi]{COMPLETED BY THE TYPESETTER}
\sdatatype{.pdf}
\sdescription{Supplementary Material contains the entire dataset with normalized wind-power production, the simulation-based results, and the complete set of empirical pointwise confidence bands for wind power production -- all corresponding to the forecast provider A.}
\end{supplement}
